---
title: "HW_MLR"
author: "경제학과 2020110210 공소연"
date: "2022-10-11"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1: Check the first 3 rows of this dataset.

```{r 1}
state.df <- data.frame(state.x77)

#Q1
head(state.df, 3)
```

## Q2: Create a new data frame using variable “Murder”, “Population”, “Illiteracy”, “Income” and “Frost” and check it.

```{r 2}
selected.var <- c(5,1,3,2,7)
stat.df <- state.df[selected.var]
str(stat.df)
```

## Q3: Conduct a multiple regression to predict the dependent variable “Murder” using all other variables as the independent variables and show the results.

```{r 3}
# partition data
set.seed(1)
train.index <- sample(c(1:50), 30)
train.df <- stat.df[train.index,]
valid.df <- stat.df[-train.index,]

stat.lm <- lm(Murder~., data = train.df)
options(scipen =999)
summary(stat.lm)
```

## Q4: Use stepwise method to select independent variables and conduct multiple regression with the selected independent variables.

```{r 4}
stat.lm.step <- step(stat.lm, direction = "both")
summary(stat.lm.step)
```

## Q5: Compare the results in Q3 and Q4.

```{r 5}
coef(stat.lm)
coef(stat.lm.step)

stat.lm.pred <- predict(stat.lm, valid.df)
stat.lm.step.pred <- predict(stat.lm.step, valid.df)

# 모델의 평가측도 계산
library(forecast)
accuracy(stat.lm.pred, valid.df$Murder)
accuracy(stat.lm.step.pred, valid.df$Murder) 

data.frame("Predicted" = stat.lm.pred,
           "Actual" = valid.df$Murder,
           "Residual" = valid.df$Murder - stat.lm.pred)

data.frame("Predicted" = stat.lm.step.pred,
           "Actual" = valid.df$Murder,
           "Residual" = valid.df$Murder - stat.lm.step.pred)
```