---
title: "HW_PCA"
author: "공소연"
date: "2022-09-24"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1: Load “decathlon2” dataset and create a new dataset excluding the “Rank” and “Competition” variables.


```{r q1}
library(factoextra)
data("decathlon2")
View(decathlon2)

data <- decathlon2[,-c(11, 13)]
```


## Q2: Use the “Points” variable as the dependent variable and create the independent variable(x) and dependent 

```{r q2}
y <- data[,c(11)]
x <- data[,c(1:10)]
```


## Q3: Conduct a principal component analysis using independent variable set and check the importance of components.

```{r q3}
pcs <- prcomp(na.omit(x), scale. = T, center=T)
summary(pcs)
pcs$rotation
```


## Q4: Choose some components to conduct a regression analysis to predict the dependent variable. How many components did you choose? Explain.

```{r p4}
pcs$x
pcs_scores <- pcs$x[,1:5]
model <- lm(y~pcs_scores)
```
